Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-29 cogsci2016/paper.tex
discussion
corrections

	We provide a measure of the different types of behaviors with the sticks and the object during exploration. 
	We categorize the behaviors into three types.
	In the first category ($hand$) are mouvements of the arm that did not grab any stick and thus not moved the out-of-reached object.
	The second category ($stick$) are mouvements that did grab one of the two sticks but did not touch the object with it.
	The third category ($object$) contains the mouvements where both a stick was grabbed and the object was moved by the stick.
	Fig. \ref{res_ow} shows the prototypical evolution of the proportion of the three categories of behavior along the $100000$ iterations for conditions H-GR-AMB and H-P-AMB.
    We performed a more detailed analysis by counting the trials where the evolution of the three types of behaviors were similar to the one of Fig. \ref{res_ow}(b).
    A structure was considered similar if it validated each of the following criteria:
    behaviors of categories $stick$ and $object$ increase quikly from $0$ to more than $10\%$ (potentially after an initial phase with a steady low value), 
    and are followed by a plateau (steady curve with small slope) with no abrupt changes, and behaviors of category $object$ start to raise at least $1000$ iterations after $stick$ started to raise.
    We counted no structures of that type in Flat conditions, $7$ for H-GR-AMB, $60$ for H-RMB, $70$ for H-P-AMB and $79$ for H-P-AMB-ATC.
    Also, the median number of abrupt changes (steady change of more than $10\%$) in conditions F-RmB, F-RGB, H-RMB, H-P-AMB, H-GR-AMB and H-P-AMB-ATC was respectively $0$, $1$, $2$, $2$, $6$, $1$, 
    with a significant difference between condition H-GR-AMB and the others (Mann-Whitney U tests, $p<0.0001$).

	\begin{table}[!ht]
		\small
		\begin{center} 
		\caption{Behavioral analysis} 
		\label{sample-table} 
		\vskip 0.12in
		\begin{tabular}{| c | c | c |} 
			\hline
			Condition  &  \begin{tabular}{@{}c@{}}Number of Trials \\ validating criteria\end{tabular}   & \begin{tabular}{@{}c@{}}Median number of  \\ Abrupt changes \end{tabular}\\
			\hline
			F-RmB        &    0 &  0\\
			F-RGB        &    0 &  1\\
			H-RMB        &   60 &  2\\
			H-P-AMB      &   70 &  2\\
			H-GR-AMB     &    7 &  6\\
			H-P-AMB-ATC  &   79 &  1\\
			\hline
		\end{tabular} 
		\end{center} 
	\end{table}

@@

	%\begin{figure}[ht]
		%\centering
		%\includegraphics[width=7cm]{./include/nbc.pdf}
		%\caption{Number of abrupt behavioral changes}
		%\label{res_nbc}
	%\end{figure}

@@

	Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H-P-AMB and H-P-AMB-ATC.
	In those conditions, model $4$ learns a mapping between $S_{Object}$ and $S_{Boxes}$. 
	When this model is babbling, it chooses a random goal $s_b \in S_{Boxes}$ and infers the best object position $s_o$ to reach $s_b$.
	To reach $s_o$, one of the tools ($Stick_1$ with model $3$ or $Stick_2$ with model $6$) is chosen. 
	We plot all those choices, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, in one figure for each of the two conditions.
	We can see two very different choice structures.
	However, goal that can be reached with both tools are more often chosen to be explored with the long stick in the interest-based choice of condition H-P-AMB-ATC than in competence-based choice of condition H-P-AMB.

@@

	\subsection{Structure of the evolution of behavior}

		Results show different structures of behavior evolution in the different conditions.
		F-RGB shows 
		H-GR-AMB shows successive behavioral steps with abrupt changes.
		Random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviors, 
		but random model babbling explores slightly less the object position.
		In this setup, the difference is more on the cognitive or intentional level, as active model babbling monitors the progress on each model whereas random model babbling do not, than on a quantitative level, 
		because here all models are still useful to explore.
		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, then active model babbling would
		make a key difference on a quantitative exploration point of view, and on the structure of the evolution of the measured behaviors.

>>>>

	\subsection{Structure of the evolution of behaviors}

		We provide a measure of the different types of behaviors with the sticks and the object during exploration. 
		We categorize the behaviors into three types.
		In the first category ($hand$) are mouvements of the arm that did not grab any stick and thus did not move the out-of-reached object.
		The second category ($stick$) are mouvements that did grab one of the two sticks but did not touch the object with it.
		The third category ($object$) contains the mouvements where both a stick was grabbed and the object was moved by the stick.
		Fig. \ref{res_ow} shows the prototypical evolution of the proportion of the three categories of behavior along the $100000$ iterations for conditions H-GR-AMB and H-P-AMB.
		We performed a more detailed analysis by counting the trials where the evolution of the three types of behaviors were similar to the one of Fig. \ref{res_ow}(b).
		A structure was considered similar if it validated each of the following criteria:
		behaviors of categories $stick$ and $object$ increase quikly from $0$ to more than $10\%$ (potentially after an initial phase with a steady low value), 
		and are followed by a plateau (steady curve with small slope) with no abrupt changes, and behaviors of category $object$ start to raise at least $1000$ iterations after $stick$ started to raise.
		See Table \ref{table} for the results of this analysis per condition.
		Also, the median number of abrupt changes across trials for each condition are reported in the same table (as the sum of steady changes of more than $10\%$ in the three behaviors).
		with a significant difference between condition H-GR-AMB and the others (Mann-Whitney U tests, $p<0.0001$).

		\begin{table}[!ht]
			\small
			\begin{center} 
			\caption{Behavioral analysis} 
			\label{table} 
			\vskip 0.12in
			\begin{tabular}{| c | c | c |} 
				\hline
				Condition  &  \begin{tabular}{@{}c@{}}Number of Trials \\ validating criteria\end{tabular}   & \begin{tabular}{@{}c@{}}Median number of  \\ Abrupt changes \end{tabular}\\
				\hline
				F-RmB        &    0 &  0\\
				F-RGB        &    0 &  1\\
				H-RMB        &   60 &  2\\
				H-P-AMB      &   70 &  2\\
				H-GR-AMB     &    7 &  6\\
				H-P-AMB-ATC  &   79 &  1\\
				\hline
			\end{tabular} 
			\end{center} 
		\end{table}

@@

	\subsection{Exploration efficiency}

@@

	\subsection{Structure of tool choice}

		Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H-P-AMB and H-P-AMB-ATC.
		In those conditions, model $4$ learns a mapping between $S_{Object}$ and $S_{Boxes}$. 
		When this model is babbling, it chooses a random goal $s_b \in S_{Boxes}$ and infers the best object position $s_o$ to reach $s_b$.
		To reach $s_o$, one of the tools ($Stick_1$ with model $3$ or $Stick_2$ with model $6$) is chosen. 
		We plot all those choices model $4$ made during exploration, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, in one figure for each of the two conditions.
		We can see two very different choice structures.
		However, goal that can be reached with both tools are more often chosen to be explored with the long stick in the interest-based choice of condition H-P-AMB-ATC than in competence-based choice of condition H-P-AMB.

@@

	\subsection{Structure of the evolution of behaviors}

		Results show different structures of behavior evolution in the different conditions.
		H-GR-AMB shows successive behavioral steps with abrupt changes.
		Random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviors, 
		but random model babbling explores slightly less the object position.
		In this setup, the difference is more on the cognitive or intentional level, as active model babbling monitors the progress on each model whereas random model babbling do not, than on a quantitative level, 
		because here all models are still useful to explore.
		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, then active model babbling would
		make a key difference on a quantitative exploration point of view, and on the structure of the evolution of the measured behaviors.
